Type cones of $\b{g}$-vector fans

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes

\begin{proposition}
\label{prop:exchangeablePairsNKC}
Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
\begin{enumerate}[(i)]
\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
\end{proposition}

@@

The quivers of this family is particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.
Note that this family already contains a lot of relevant examples, including:
\begin{itemize}
\item classical associahedra
\item grid associahedra
\item dissection associahedra
\end{itemize}
\vincent{More explicit. TODO}

@@

We checked on some (but probably not enough) small gentle quivers the following properties:
\begin{enumerate}
\item Any $c$-vector (\ie distinguishable string) is the direction of at least one extremal exchangeable pair.
\item Consider a distinguishable string~$\sigma$. Let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$. If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$. These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
\item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
\end{enumerate}

@@

\begin{proposition}
 Let~$X,Y\in \ind(\cat)$ be such that~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.  Let 
 \[
  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X \quad \textrm{and} \quad Y\xrightarrow{} E' \xrightarrow{} X \xrightarrow{h'} \susp Y
 \]
 be triangles with~$h$ and~$h'$ non-zero (these triangles are unique up to isomorphism).  Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
 \begin{proof}
  \pg{TO DO, Vincent: definition of positive mutation?}
 \end{proof}
\end{proposition}

>>>>

\begin{proposition}
\label{prop:exchangeablePairsNKC}
Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
\begin{enumerate}[(i)]
\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facets~$F $ and~$F'$.
\yann{This needs more assumptions.  Move to another proposition.}
\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
\end{proposition}

@@

The quivers of this family are particularly well-behaved: they avoid all pathologies of \cref{rem:exchangeablePairsNKC} and we will prove that the type cone of their non-kissing fan happens to be simplicial.\pg{Need to exclude two-cycles, else false.}
Note that this family already contains a lot of relevant examples, including:
\begin{itemize}
\item classical associahedra
\item grid associahedra
\item dissection associahedra
\end{itemize}
\vincent{More explicit. TODO}

@@

We checked on some (but probably not enough) small gentle quivers the following properties:
\begin{enumerate}
\item Any $c$-vector (\ie distinguishable string) is the direction of at least one extremal exchangeable pair.
\item Consider a distinguishable string~$\sigma$. Let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$. If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$. These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.\pg{The conjecture is the word ``unique''.}
\item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
\end{enumerate}

@@

\begin{proposition}
 Let~$X,Y\in \ind(\cat)$ be such that~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$.  Let 
 \[
  X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X 
 \]
 be triangle with~$h$ non-zero (this triangle is unique up to isomorphism).  Then~$\CC(Y)$ is obtained by performing a positive mutation on~$\CC(X)$ in some seed if and only if~$h\in (\susp T)$.
 \begin{proof}
  \pg{TO DO, Vincent: definition of positive mutation?}
 \end{proof}
\end{proposition}
